Interval Probability for Fuzzy Quantum Theories

### 2016-07-22 prob.tex
From: Tai, Yu-Tsung Sent: Friday, July 22, 2016 3:15 To: Hanson, Andrew J. <hansona@indiana.edu> Cc: Ortiz, Gerardo <ortizg@indiana.edu>; Amr A. Sabry (sabry@indiana.edu) <sabry@indiana.edu> Subject: RE: Yu-Tsung made changes in your shared folders (fwd)
I added a citation to Choquet's paper, and I put his paper in Dropbox
because I think it is too big to put in ShareLaTeX...

Last week, we discussed Gleason's theorem is a generalization of the
Radon-Nikodym theorem in classical case, and we associate a quantum
real-valued and interval-valued probability measures with a "belong to"
relation...

>>>>

Although there is no easy Radon-Nikodym theorem, an interval-valued
probability measure can still be understood by its relation with real-valued
probability measures, like we constructed example~\ref{ex3} from
example~\ref{ex1}. In general, a \emph{core} of an interval-valued
probability measure~$\bar{\mu}:\events\rightarrow\mathscr{I}$ is
a set of real-valued probability measures~$\pmeas:\events\rightarrow[0,1]$
such that $\pmeas\left(E\right)\in\bar{\mu}\left(E\right)$ for all
$E\in\events$~\cite{GilboaSchmeidler1994,Marinacci1999,Teran2014}.

\yutsung{The following theorem proved that a wide variety of interval-valued
probability measures can be associated with real-valued probability
measures.

\begin{thm}[Shapley~\cite{Shapley1965,GilboaSchmeidler1994}]
Every convex interval-valued probability measure has a nonempty core,
where an interval-valued probability measure~$\bar{\mu}:\events\rightarrow\mathscr{I}$
is convex if $\bar{\mu}\left(E\right)=\left[l\left(E\right),r\left(E\right)\right]$
and $l\left(E_{1}\cup E_{2}\right)\le l\left(E_{1}\right)+l\left(E_{2}\right)-l\left(E_{1}\cap E_{2}\right)$
for all $E_{1},E_{2}\in\events$.\qed\end{thm}

In particular, Dempster-Shafer probability measures are all convex
and have nonempty cores. Need to verify whether general interval-valued
probability measures must have a core or find a counterexample.}
